Verifying Demonstrations

### 2018-11-16 paper/privacy-properties.tex
Edits verifiability and privacy properties, pseudonyms

Thus, in our context the crucial property is therefore privacy.
More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Finally, any temporary identifiers such as pseudonyms should only be reused 
when strictly necessary for the fulfillment of verifiability properties listed 
in \cref{verifiability-properties} to prevent inference on long-term identities 
by repeated samples and side information.

@@

>>>>

Thus, in our context the crucial property is therefore privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the cause identifier 
\(\cid\).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (\eg 
from a different protest).

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}

Finally, any temporary identifiers, such as pseudonyms, should only be reused 
when strictly necessary for the fulfillment of verifiability properties (in 
\cref{verifiability-properties}) to prevent inference on long-term identities 
by repeated samples and side information.

@@

In light of these definitions, we note that \cref{CountOnce} can be rephrased 
in terms of pseudonyms as follows:
\begin{enumerate}
  \item[V1.3.] \emph{Counted only once}:
    A protester can create \emph{only one} pseudonym per protest, this 
    pseudonym is unique except with negligible probability.
\end{enumerate}
